Alternative Methods for Implementing Explicit and Finding Implicit Sharing in embedded DSLs

### 2022-12-16 paper/paper.tex
updated acknowledgements
moved christopher to the back

% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following two lines
% to display URLs in blue roman font according to Springer's eBook style:
%\usepackage{color}
%\renewcommand\UrlFont{\color{blue}\rmfamily}
%
\begin{document}
\lstset{language=haskell}
%
\title{Alternative Methods for Implementing
    Explicit and Finding Implicit Sharing in embedded DSLs}
%
\titlerunning{Alternative Explicit and Implicit Sharing}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Curtis D'Alves \and
Christopher Kumar Anand \and
Lucas Dutton \and
Steven Gonder
}
%
\authorrunning{C. D'Alves et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{McMaster University, 1280 Main St W Hamilton, Canada}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
  Detection of sharing is known challenge for implementers of embedded domain
  specific languages (DSLs). There are many solutions, each with their
  advantages and drawbacks. Many solutions are based on observable sharing, that
  requires either a monadic interface or use of unsafe referencing, e.g.,
  Data.Reify. Monadic interfaces are consider unsuitable for domain experts, and
  the use of unsafe referencing leads to fragile software.

@@

\subsubsection{Acknowledgements} We thank NSERC and IBM Canada for supporting this work.
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
\bibliographystyle{splncs04}
\bibliography{references}

>>>>

% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following two lines
% to display URLs in blue roman font according to Springer's eBook style:
%\usepackage{color}
%\renewcommand\UrlFont{\color{blue}\rmfamily}
%
\begin{document}
\lstset{language=haskell}
%
\title{Alternative Methods for Implementing
    Explicit and Finding Implicit Sharing in embedded DSLs}
%
\titlerunning{Alternative Explicit and Implicit Sharing}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Curtis D'Alves \and
Lucas Dutton \and
Steven Gonder \and
Christopher Kumar Anand
}
%
\authorrunning{C. D'Alves et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{McMaster University, 1280 Main St W Hamilton, Canada}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
  Detection of sharing is known challenge for implementers of embedded domain
  specific languages (DSLs). There are many solutions, each with their
  advantages and drawbacks. Many solutions are based on observable sharing, that
  requires either a monadic interface or use of unsafe referencing, e.g.,
  Data.Reify. Monadic interfaces are consider unsuitable for domain experts, and
  the use of unsafe referencing leads to fragile software.

@@

\subsubsection{Acknowledgements} We thank NSERC and IBM Canada Advanced Studies for supporting this work.
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
\bibliographystyle{splncs04}
\bibliography{references}
